Programs Performance Analysis Toolkit

### 2013-09-30 keynote/Keynote.tex
Add Overview

>>>>

\begin{frame}
\frametitle{Overview}

	\begin{itemize}
		\item A lot of recent research: see C.\,Dubach, G.\,Fursin, B.\,C.\,Lee, W.\,Wu
		\item In particular, there's \textit{cTuning} public repository for research and corresponding program \textit{Collective Mind} run by G.\,Fursin
		\item This work is about modeling of performance of general-purpose computer programs with feature ranking by means of \textit{Earth Importance} and regression by means of \textit{k-Nearest Neighbors} and \textit{Earth Regression}. We try to accomplish automatic detection of relevant features.
	\end{itemize}
\end{frame}
